Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-05-04 pldi14/sec-formal.tex
Spelling: it's de Bruijn, damn it

We formalize the simply-typed lambda calculus we presented using
typed de Brujin indexes to handle binding, because it takes well
advantage of Agda's support for type refinement in pattern
matching. On top of that, we implement a HOAS-like frontend, that
we use for writing specific terms.
The domains for our denotational
semantics are Agda types, and semantic values are simply Agda
values---in other words, we give a denotational semantics in
terms of type theory.
%
This allows us to state the specification of differentiation
directly in the semantic domain, and take advantage of Agda's
support for equational reasoning between Agda functions.

>>>>

We formalize the simply-typed lambda calculus we presented using
typed de Bruijn indexes to handle binding, because it takes well
advantage of Agda's support for type refinement in pattern
matching. On top of that, we implement a HOAS-like frontend, that
we use for writing specific terms.
The domains for our denotational
semantics are Agda types, and semantic values are simply Agda
values---in other words, we give a denotational semantics in
terms of type theory.
%
This allows us to state the specification of differentiation
directly in the semantic domain, and take advantage of Agda's
support for equational reasoning between Agda functions.
